---
title: "Homework 04 - Data Classes w. forcats & lubridate"
author: "Louis Quigley"
date: "3/9/23"
output: pdf_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro) 
library(lubridate)
```

## Exercises

### Exercise 1
```{r}
#frame_size_cm 
numeric <- c(52,54,56,58,60)
#bike_attachments 
character <- c("grips", "lights", "rack", "fenders", "bell")
#wheel_size
mixed <- c(27, "700c", "650b", 26, 20)
```
### Exercise 2

```{r label-me1 , eval = F}
data_frame <- bind_cols("numeric" = numeric, "character" = character, "mixed" = mixed)
data_frame
```
the data frame is a `r typeof(data_frame)` and a `r class(data_frame)`.  
### Exercise 3

```{r fake-dataframe, eval = F}
#frame_size_cm 
numeric <- c(52,54,56,58,60)
#bike_attachments 
character <- c("grips", "lights", "rack", "fenders", "bell")
#wheel_size
mixed <- c(27, "700c", "650b", 26)
```

```{r label-me1 , eval = F}
data_frame <- bind_cols("numeric" = numeric, "character" = character, "mixed" = mixed)
data_frame
```
Data frames must have the same number of observations in each variable. Since the mixed frame only has four variables, r is not able to bind the observations into a colmn. 
### Exercise 4

```{r label-me2, eval = F}
my_list <- list("numeric" = numeric, "character" = character, "mixed" = mixed)
my_list
```
Lists can have a different number of observations per column, unlike data frames. 
### Exercise 5

```{r earthquakes-factors}
earthquakes %>% 
  ggplot(aes(x = month)) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```
The "month" variable is being ordered alphabetically. This creates a graph that is out of chronological order. 
### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 10 here.
