---
title: "Homework 04 - Data Classes w. forcats & lubridate"
author: "Louis Quigley"
date: "3/9/23"
output: pdf_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro) 
library(lubridate)
```

## Exercises

### Exercise 1
```{r}
#frame_size_cm 
numeric <- c(52,54,56,58,60)
#bike_attachments 
character <- c("grips", "lights", "rack", "fenders", "bell")
#wheel_size
mixed <- c(27, "700c", "650b", 26, 20)
```
### Exercise 2

```{r label-me1 , eval = F}
data_frame <- bind_cols("numeric" = numeric, "character" = character, "mixed" = mixed)
___
```

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 10 here.
