---
title: "Homework 04 - Data Classes w. forcats & lubridate"
author: "Louis Quigley"
date: "3/9/23"
output: pdf_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro) 
library(lubridate)
library(glue)
```

## Exercises

### Exercise 1
```{r label-variables, eval = F}
#frame_size_cm 
numeric <- c(52,54,56,58,60)
#bike_attachments 
character <- c("grips", "lights", "rack", "fenders", "bell")
#wheel_size
mixed <- c(27, "700c", "650b", 26, 20)
```
### Exercise 2

```{r label-me1 , eval = F}
data_frame <- bind_cols("numeric" = numeric, "character" = character, "mixed" = mixed)
data_frame
```
the data frame is a `r typeof(data_frame)` and a `r class(data_frame)`.  
### Exercise 3

```{r fake-dataframe, eval = F}
#frame_size_cm 
numeric <- c(52,54,56,58,60)
#bike_attachments 
character <- c("grips", "lights", "rack", "fenders", "bell")
#wheel_size
mixed <- c(27, "700c", "650b", 26)
```

```{r label-me2 , eval = F}
data_frame <- bind_cols("numeric" = numeric, "character" = character, "mixed" = mixed)
data_frame
```
Data frames must have the same number of observations in each variable. Since the mixed frame only has four variables, r is not able to bind the observations into a colmn. 
### Exercise 4

```{r label-me2, eval = F}
my_list <- list("numeric" = numeric, "character" = character, "mixed" = mixed)
my_list
```
Lists can have a different number of observations per column, unlike data frames. 
### Exercise 5

```{r earthquakes-factors}
earthquakes %>% 
  ggplot(aes(x = month)) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```
The "month" variable is being ordered alphabetically. This creates a graph that is out of chronological order. 
### Exercise 6

```{r earthquakes-forcats-1}
earthquakes %>% 
  ggplot(aes(x = fct_infreq(month))) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```
The fct_infreq function orders the "months" variable in descending order based on its frequency of levels.  
```{r earthquakes-forcats-2}
earthquakes %>% 
  ggplot(aes(x = fct_rev(month))) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```
The fct_rev function orders the variable "month" in reverse order of its level (alphabetical order).  
```{r earthquakes-forcats-3}
earthquakes %>% 
  ggplot(aes(x = fct_inorder(month))) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```
the fct_inorder function gives the variable "month" in the original order they appear in the data. 
```{r earthquakes-forcats-4}
earthquakes %>% 
  ggplot(aes(x = month %>% fct_infreq() %>% fct_rev())) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```
The fct_infreq function orders the variable "month" by the less frequent level. 
```{r earthquakes-forcats-5}
earthquakes %>% 
  mutate(month = fct_recode(month,
                            "1" = "January",
                            "2" = "February",
                            "3" = "March",
                            "4" = "April",
                            "5" = "May",
                            "6" = "June",
                            "7" = "July",
                            "8" = "August",
                            "9" = "September",
                            "10" = "October",
                            "11" = "November",
                            "12" = "December")) %>% 
  ggplot(aes(x = factor(as.numeric(month)))) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```
The fct_recode function is remapping the months to numeric values so they are arranged in chronological order on the graph. 
### Exercise 7

```{r earthquake-dates}
earthquakes_new <- earthquakes %>% 
  mutate(date = glue("{year} {month} {day}")) %>% 
  relocate(date)
print(earthquakes_new)
```
the mutate() function is creating a new variable "data" by combining year, month, and day, variables. The relocate() function is moves blocks of columns at once. 
### Exercise 8

```{r earthquake-1993}
earthquakes_new %>%
  filter(year == 1933) %>%
  ggplot(aes(date, richter)) +
  geom_point()
```
The dates are out of chronological order! They appear on the graph in the inverse order that they are listed in the tibble. 
### Exercise 9

```{r earthquakes-dates2, eval = T}
library(lubridate)

earthquakes %>%
  mutate(date = ymd(glue("{year}-{month}-{day}"))) %>%
  relocate(date) %>%
  ggplot(aes(date, richter)) +
  geom_point()
```
the ymd() function converts the dates from characters into the class date in a "year, month, day" format. 

### Exercise 10

Remove this text, and add your answer for Exercise 10 here.
