---
title: "Lab 04 - Data Type Coercion"
author: "Louis Quigley"
date: "3/7/23"
output: pdf_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(openintro)
```

## Exercises

### Exercise 1

```{r echo = F}
1
1L
"C"
```
1 is a `r typeof(1)`.  
1L is an `r typeof(1L)`.  
"C" is a `r typeof("C")`.  
```{r echo = F}
c(1, 1L, "C")
```
The second code chunk is a vector and is displayed as variables in a row
```{r echo = F}
typeof(c(1, 1L, "C"))
```
The vector has to be of the same type and the numbers are interpreted as characters, because "C" cannot be expressed an a numerical.  
### Exercise 2

```{r echo = F}
1:3
5
```
1:3 is type `r typeof(1:3)` and displays the numbers 1 through 3 as `r typeof(1:3)`.  
5 is type `r typeof(5)`
```{r echo = F}
typeof(c(1:3, 5))
```
The values 1:3 are integers, but since 5 is a double, the vector is treated as all doubles.  
### Exercise 3

```{r echo = F}
3 
FALSE
T
```
3 is the type `r typeof(3)`.  
FALSE and T are the type `r typeof(FALSE)`.
```{r echo = F}
typeof(c(3, FALSE, T))
```
This vector contains both numerical and logical data types. Because there is a numerical value (3), all data types must be coerced from logical data types to the higher-level data type numerical. The type is displayed as `r typeof(c(3, FALSE, T))` because double, is the lowest level data type common to all data.  
### Exercise 4

```{r echo = F}
TRUE
as.numeric(TRUE)
```
TRUE is of type `r typeof(TRUE)`, but as.numeric specifies that "TRUE" is to be a `r typeof(as.numeric(true))`.  
```{r echo = F}
typeof(c(TRUE, as.numeric(TRUE)))
```
Since as.numeric(TRUE) specifies that it should be read as a numeric, all species in the vector must be treated as numerics and in this case as doubles. 
### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 9 here.
