---
title: "Lab 04 - Data Type Coercion"
author: "Louis Quigley"
date: "3/7/23"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(openintro)
```

## Exercises

### Exercise 1

```{r echo = F}
1
1L
"C"
```
1 is a `r typeof(1)`.  
1L is an `r typeof(1L)`.  
"C" is a `r typeof("C")`.  
```{r echo = F}
c(1, 1L, "C")
```
The second code chunk is a vector and is displayed as variables in a row
```{r echo = F}
typeof(c(1, 1L, "C"))
```
The vector has to be of the same type and the numbers are interpreted as characters, because "C" cannot be expressed an a numerical.  
### Exercise 2

```{r echo = F}
1:3
5
```
1:3 is type `r typeof(1:3)` and displays the numbers 1 through 3 as `r typeof(1:3)`.  
5 is type `r typeof(5)`
```{r echo = F}
typeof(c(1:3, 5))
```
The values 1:3 are integers, but since 5 is a double, the vector is treated as all doubles.  
### Exercise 3

```{r echo = F}
3 
FALSE
T
```
3 is the type `r typeof(3)`.  
FALSE and T are the type `r typeof(FALSE)`.
```{r echo = F}
typeof(c(3, FALSE, T))
```
This vector contains both numerical and logical data types. Because there is a numerical value (3), all data types must be coerced from logical data types to the higher-level data type numerical. The type is displayed as `r typeof(c(3, FALSE, T))` because double, is the lowest level data type common to all data.  
### Exercise 4

```{r echo = F}
TRUE
as.numeric(TRUE)
```
TRUE is of type `r typeof(TRUE)`, but as.numeric specifies that "TRUE" is to be a `r typeof(as.numeric(TRUE))`.  
```{r echo = F}
typeof(c(TRUE, as.numeric(TRUE)))
```
Since as.numeric(TRUE) specifies that it should be read as a numeric, all species in the vector must be treated as numerics and in this case as doubles. 
### Exercise 5

```{r echo = F}
NA
FALSE
as.logical(1)
```
All data dypes are `r typeof(NA)`. as.logical(1) turns into TRUE, which is a logical type, because TRUE is defined numerically as "1".
```{r echo = F}
typeof(c(NA, FALSE, as.logical(1)))
```
In the vector, all data types are `r typeof(as.logical(1))`, therefore the whole vector is of type `r typeof(NA)`.  
### Exercise 6

```{r echo = F}
1L
0
1L / 0
"A"
```
1L is of type `r typeof(1L)`.  
0 is of `r typeof(0)`.  
In 1L/0, the 1L is type `r typeof(1L)`, but the 0 is type `r typeof(0)`. Together 1L/0 is of type `r typeof(1L/0)`.  
"A" is of type `r typeof("A")`.  
```{r echo = F}
typeof(c(1L / 0, "A"))
```
The data type is `r typeof(c(1L/0, "A"))`, because even though 1L/0 is of data type (`r typeof(1L/0)`, "A" is of data type `r typeof("A")`, which R must then interpret the whole vector as type `r typeof("A")`.  
### Exercise 7

```{r}
glimpse(earthquakes)
```


### Exercise 8

the year, day, and deaths variables can be coerced from doubles into integers without losing information, because year, day, and deaths are expressed as whole numbers and the value does not change between the types "double" or "integer."

### Exercise 9

as.character(1902) would take away the order of the years, which would make
the years not be ordered chronologically on the graph. 

### Exercise 10 -.5

```{r label-me, eval = T}
earthquakes %>% 
  mutate(major = case_when(
    richter > 7.5 ~ TRUE,
    TRUE ~ FALSE
  )) %>% 
  mutate(major = as.numeric(major)) %>% 
  filter(major == 1)
```
