---
title: "Lab 04 - Data Type Coercion"
author: "Louis Quigley"
date: "3/7/23"
output: pdf_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(openintro)
```

## Exercises

### Exercise 1

```{r echo = F}
1
1L
"C"
```
1 is a `r typeof(1)`.
1L is an `r typeof(1L)`.
"C" is a `r typeof("C")`.
```{r echo = F}
c(1, 1L, "C")
```
The second code chunk is a vector and is displayed as variables in a row
```{r echo = F}
typeof(c(1, 1L, "C"))
```
The vector has to be of the same type and the numbers are interpreted as characters, because "C" cannot be expressed an a numerical. 
### Exercise 2

Remove this text, and add your answer for Exercise 2 here.

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 9 here.
